---
title: "Twitter analyses"
author: "Yiluan Song"
date: "2023-04-19"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, cache = TRUE)
source("script/setup.R")
```

## Preprocess data
# combine csv files into rds

```{r}
source("script/combine_csv.R")
df_compiled %>% head()
```

# Reverse geo-encoder

```{r}
source("script/reverse_geocoder.R")
df_geo_all %>%
  filter(us_state == "us") %>%
  select(user_location, state, us_state) %>%
  head()
```

Among `r df_compiled_geo %>% nrow()` records, `r df_compiled_geo %>% filter(us_state == "us") %>% nrow()` can be identified to be within the US, and `r df_compiled_geo %>% filter(!is.na(state)) %>% nrow()` can be identified to US states.

# Filter and clean data
Filtering criteria:
- no duplicated unique id
- posted in English
- have the exact keyword "pollen" in the cleaned text (not a part of a longer word, not in tags, not in urls)
- identified to be within the US
Cleaning steps (original text still kept):
- remove line breaks
- remove url
- remove tag
- remove "RT" at the start
- remove non-words
- convert character encoding from UTF-8 to ASCII

```{r}
source("script/preprocessing.R")
p_pie_type
```

There were `r df_type %>% nrow()` tweets that satisfied all criteria and were used in the following analyses.

## Temporal analysis
# Twitter time series

```{r}
source("script/twitter_time_series.R")
p_tw_ts
p_tw_ts_fs
p_user_num
```
# NAB time series
```{r}
source("script/nab_data.R")
p_nab_map
source("script/nab_time_series.R")
p_nab_ts
p_nab_ts_fs
p_nab_ts_sd
```

# Compare time series
```{r}
source("script/compare_time_series.R")
p_ts_comp
p_ts_corr
p_ts_peak_corr
```

# Spatial analysis

```{r}
source("script/twitter_spatial_pattern.R")
p_tw_map
source("script/nab_spatial_pattern.R")
p_nab_map_station
p_nab_map_state
source("script/compare_spatial_pattern.R")
p_sp_corr
```
## Spatiotemporal analysis
```{r}
source("script/twitter_spatiotemporal.R")
p_tw_pheno_state
source("script/nab_spatiotemporal.R")
p_nab_pheno_state
source("script/compare_spatiotemporal.R")
p_doy_state
```

## Content analysis
# Frequent words
```{r}
source("script/frequent_words.R")
p_keyword_bar
p_keyword_cloud
```
# Topic modeling
```{r}
source("script/topic_modeling.R")
p_perplexity
p_topic
df_text_class %>%
  filter(topic == 3) %>%
  sample_n(20)
```

# Sentiment analysis
```{r}
source("script/sentiment_analysis.R")
p_senti_all
p_senti_topic
p_senti_all_fine
p_senti_topic_fine
```

# Ideological bias
```{r}
source("script/group_sample_coding.R")
source("script/get_ideology.R")
source("script/analyze_ideology.R")
df_group_sample_size
df_ideo_summ
p_ideo_density
p_ideo_cond1
p_ideo_cond2
```

# Echo chamber

```{r}
source("script/echo_chamber.R")
p_net
p_net_reg
```



