---
title: "01 Preprocessing"
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_knit$set(root.dir = here::here()) # knit from project directory
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  cache = T,
  comment = "#>",
  warning = F,
  message = F,
  out.width = "100%",
  fig.align = "left"
)
```

```{r setup}
library(phenotwitter)
theme_set(ggthemes::theme_few())
```

# Combine csv files into rds

```{r, eval = F}
path_compile <- read_tweet_csv()
```

```{r, eval = F}
df_compiled <- read_tweet(geo = F)
set.seed(1)
```
Total number of tweets in the dataset `r df_compiled %>% nrow()`.

# Reverse geo-encoder

```{r, eval = F}
df_summ_geo <- summarize_geo_info(df_tweet = df_compiled)
```
Percentage of users with location info is `r df_summ_geo$perc`.

```{r, eval = F}
path_geo <- tidy_geo(df_tweet = df_compiled)
```

```{r, eval = F}
df_compiled_geo <- read_tweet(geo = T)
```

Among `r df_compiled_geo %>% nrow()` records, `r df_compiled_geo %>% filter(us_state == "us") %>% nrow()` can be identified to be within the US, and `r df_compiled_geo %>% filter(!is.na(state)) %>% nrow()` can be identified to US states.

# Filter and clean data
Filtering criteria:
- no duplicated unique id
- posted in English
- have the exact keyword "pollen" in the cleaned text (not a part of a longer word, not in tags, not in urls)
- identified to be within the US
Cleaning steps (original text still kept):
- remove line breaks
- remove url
- remove tag
- remove "RT" at the start
- remove non-words
- convert character encoding from UTF-8 to ASCII

```{r, eval = F}
df_tweet <- tidy_tweet_clean(df_compiled_geo = df_compiled_geo)
usethis::use_data(df_tweet)
```

```{r, eval = F}
df_tweet %>%
  select(text) %>%
  sample_n(10)
summ_tweet(df_tweet = df_tweet)
```

There were `r df_tweet %>% nrow()` tweets that satisfied all criteria and were used in the following analyses. There were `r df_tweet %>% filter(!is.na(state)) %>% nrow()` tweets among these that could be resolved to states.

```{r, eval = F}
plot_tweet_type(df_tweet = df_tweet, save = T)
```
